Injrury Outcomes - WHW matrices

### 2022-01-19 injury_tables.Rmd
Save injury outputs in excel sheet. Ref #86

### True distances in a single file
```{r }
true_distances <- list()
for (city in cities) { # Loop for each city
  true_distances[[city]] <- io[[city]]$true_dist %>% 
    pivot_longer(!stage_mode, names_to = "scenario", values_to = "distance") %>% 
    mutate(city = city)
}
true_distances_df <- bind_rows(true_distances)
readr::write_csv(true_distances_df, 'results/multi_city/whw_matrices/distances.csv')
```

>>>>

### True distances in a single file
```{r }
true_distances <- list()
for (city in cities) { # Loop for each city
  true_distances[[city]] <- io[[city]]$true_dist %>% 
    pivot_longer(!stage_mode, names_to = "scenario", values_to = "distance") %>% 
    mutate(city = city)
}
true_distances_df <- bind_rows(true_distances) %>% 
  mutate(scenario = case_when(
    scenario == "Scenario 1" ~ "Bicycling", 
    scenario == "Scenario 2" ~ "Driving",
    scenario == "Scenario 3" ~ "Public Transport",
    scenario == "Baseline" ~ "Baseline"))
readr::write_csv(true_distances_df, 'results/multi_city/whw_matrices/distances.csv')
```

### Write all injury tables in a single excel sheet
```{r}

# Export injury datasets in a single excel sheet
path_inj_wb <- "results/multi_city/inj/inj_data.xlsx"
writexl::write_xlsx(list(whw = whw_list %>% filter(str_mode != 'Total'),
                         injury_risks_per_billion_kms = rd,
                         injury_risks_per_100k  = injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'),
                         true_distances = true_distances_df),
                    path = path_inj_wb)
